Security Audit of Safeplug ``Tor in a Box''

### 2014-03-02 w2sp/report.tex
made changes to figure, graph, arrangement
Fixes to the remaining todos from todo.txt

Pogoplug made use of good security principles by using auditable open source software on their device, and has a laudable goal of making online security the standard for more users.  However, even if the engineering vulnerabilities are fixed with proper authentication for modifying Safeplug settings, the incompleteness of the provided anonymity and risks of adding an additional box to the trusted inside of the home network mean that there is little reason to use the Safeplug over the Tor Browser Bundle.

\begin{figure*}
\centering
\includegraphics[width=.75\textwidth]{instructions2}
\caption{Setup instructions (and the only documentation) that came in the box with the Safeplug. Pogoplug highlights the ease of installing the device but does not give a clear indication of how the Safeplug functions.}
\label{fig:instructions}
\end{figure*}

@@

\subsection{Activation and Setup}
The first step was to plug Safeplug into our router and activate our device.  Our instructions are shown in Figure~\ref{fig:instructions}.  We followed them, activated our device, and then ended on the configurations page.  The configurations page has a combination of platforms and browsers, with a different set of proxy configuration instructions for each one.  The platforms presented include popular desktop and mobile platforms.  The Tor Project has an Android application, as well as the Tor Browser Bundle for Windows and OSX (and Linux, which is not supported explicitly by Pogoplug's page but is likely to have a browser with similar configuration processes to Firefox).  However, there is no existing Tor Project application for iOS.

@@

After we finished our configuration, we were taken to the Safeplug settings page.  This page is shown in Figure~\ref{fig:settings}.  This allowed us to turn Tor on/off, add white-listed websites, turn ad-blocking on/off, and turn the ability of our device to be a relay node on/off (and if on, an additional option appeared to allow the device to be an exit node).

\begin{figure}[htb]
  \centering
  \includegraphics[width=.4\textwidth]{settings_with_exit}
  \caption{Safeplug settings page.  The last button ``Allow Exit'' only appears if the relay option above has been turned on.}
  \label{fig:settings}
\end{figure}

@@

\subsection{Browser Fingerprinting}
We used Panopticlick to examine the fingerprint of a freshly installed Firefox browser running through the Safeplug proxy~\cite{panopticlick}.  Panopticlick found the browser to be unique.  Fingerprinting is another way in which websites could correlate and de-anonymize user traffic without knowing the IP address.

@@

\begin{figure*}
  \centering
  \includegraphics[width=0.7\textwidth]{graph2}
  \caption{Latency of web requests.}
  \label{fig:latency2}
\end{figure*}

@@

\subsection{Insider Attack}
Since the Safeplug has no validation or authentication on the settings page or these RPC calls, any malicious party inside the network could easily modify the settings.  Such an adversary with a computer could load the Safeplug's settings page and adjust options such as disabling Tor or adding a site to the whitelist; since this page is meant to be accessible to normal Internet users, anyone can perform this attack.  Unlike many home routers, there is no username/password combination necessary to access this page.

A more technically advanced user could send the call directly to the RPC server.  All the attacker would need to know is the IP address of the device.  It does not require SSH or discovering the (publically available) root password, or the user's new root password if they have been well-informed and adept enough to change it.  Figure \ref{disable} shows an example of the RPC version of this attack.

@@

\subsection{Gaining Access through SSH}
\label{sec:SSH}
    Another command available to the RPC server is enabling SSH to the device.  SSH instructions for Cloud Engine's other device (Pogoplug) are widely available online and an email in the Tor-talk mailing list confirms that the instructions are the same \cite{ceadmin}:
\begin{lstlisting}
curl --data ``'' http://<IP>/svc/xspctrl/enableSSHD
ssh root@<IP-of-Safeplug>
password: ceadmin
\end{lstlisting}

@@

One type of client that deserves special attention is a non-Android mobile phone user.  Although the Tor Project publishes an Android app called Orbot on the Android Market, which is supported for Android versions 2.3 and later, there are no official Tor apps for iPhones or other non-Android devices~\cite{orbot,amorbot}.  Safeplug provides proxy functionality and instructions for Safari on the iPhone; however, this would only work while the user is on that wifi network that the Safeplug routes through.  If any data is sent over the cellular network or another wifi network, then the security of Tor is lost.  Additionally, the user may have to disable the proxy whenever they move to a different network, and remember to re-enable it when they want to use Tor.  This is certainly not transparent usability.  Users who are truly concerned about anonymity online should eschew the Safeplug and purchase a device that supports the Tor Browser Bundle or other Tor Project software.

>>>>

Pogoplug made use of good security principles by using auditable open source software on their device, and has a laudable goal of making online security the standard for more users.  However, even if the engineering vulnerabilities are fixed with proper authentication for modifying Safeplug settings, the incompleteness of the provided anonymity and risks of adding an additional box to the trusted inside of the home network mean that there is little reason to use the Safeplug over the Tor Browser Bundle.  Unlike the plain Tor technology, the Tor Browser Bundle contains protections against tracking cookies and fingerprinting, making it an improvement over the privacy offerings of the Safeplug.

\begin{figure*}
\centering
\includegraphics[width=.65\textwidth]{instructions2}
\caption{Setup instructions (and the only documentation) that came in the box with the Safeplug. Pogoplug highlights the ease of installing the device but does not give a clear indication of how the Safeplug functions.}
\label{fig:instructions}
\end{figure*}

@@

\subsection{Activation and Setup}
The first step was to plug Safeplug into our router and activate our device.  Our instructions are shown in Figure~\ref{fig:instructions}.  We followed them, activated our device, and then ended on the configurations page.  The configurations page has a combination of platforms and browsers, shown in the table below, with a different set of proxy configuration instructions for each one.  The platforms presented include popular desktop and mobile platforms.  For every browser on every client device that the user wants to protect, they must set up the Safeplug as the browser's HTTP proxy and ensure that the proxy stays set up when the browser is updated or re-installed.

%\begin{table}[!t]
%\renewcommand{\arraystretch}{1.3}
%\caption{The platforms and browsers that the Safeplug settings page provides instructions for.}
%\label{table_example}
%\centering
%	\begin{tabular}{|c|c|}
%	\hline
%		Platform & Browsers \\ \hline
%		Windows	& Internet Explorer, Chrome, Firefox \\ \hline
%		OSX & Safari, Chrome, Firefox \\ \hline
%		iOS	& Safari \\ \hline
%		Android	& Chrome \\ \hline
%	\end{tabular}
%\end{table}

@@

After we finished our configuration, we were taken to the Safeplug settings page.  This page is shown in Figure~\ref{fig:settings}.  This page allows the user to set a number of options on the device, including turning Tor on/off, turning ad-blocking on/off, and turning relay node ability on/off (and if on, an additional option appeared to allow the device to be an exit node).  Additionally, the user can specify ``white-listed'' domains that will be connected to directly even if Tor is turned on, without going through the Tor network.  The Safeplug FAQ website describes this as an option for bank websites or other sites that might completely prevent logons from foreign IP addresses\cite{safeplug}.

\begin{figure*}
  \centering
  \includegraphics[width=.7\textwidth]{settings_with_exit}
  \caption{Safeplug settings page.  The last button ``Allow Exit'' only appears if the relay option above has been turned on.}
  \label{fig:settings}
\end{figure*}

@@

\subsection{Browser Fingerprinting}
We used Panopticlick to examine the fingerprint of a freshly installed Firefox browser running through the Safeplug proxy~\cite{panopticlick}.  Panopticlick found the browser to be unique, which means that websites that did fingerprinting could very accurately track, correlate, and de-anonymize user traffic without knowing the IP address or even storing a cookie.  The presence of the Safeplug, as an HTTP proxy, should be completely undetectable by the fingerprinting service by the design of HTTP making proxies transparent.  Unlike the Tor Browser Bundle, Safeplug users do not even have the fingerprints of other users of the service to help hide their fingerprints.  Allowing the user to use their own browsers significantly incrases the amount of variation and customization between users and therefore the likelihood of having a unique fingerprint.  This danger to anonymity (unlike cookies) is not even mentioned in the Safeplug FAQ page~\cite{safeplug}.

@@

\begin{figure*}
  \centering
  \includegraphics[width=0.5\textwidth]{latencygraph}
  \caption{Latency of web requests.}
  \label{fig:latency2}
\end{figure*}

@@

\subsection{Insider Attack}
Since the Safeplug has no validation or authentication on the settings page or these RPC calls, any malicious party inside the home network could easily modify the settings.  Such an adversary with a computer could load the Safeplug's settings page and adjust options such as disabling Tor or adding a site to the whitelist; since this page is meant to be accessible to normal Internet users, anyone can perform this attack.  Unlike many home routers, there is no username/password combination necessary to access this page.  A more technically advanced user could send the call directly to the RPC server.  All the attacker would need to know is the IP address of the device.  Figure \ref{disable} shows an example of the RPC version of this attack.

Since the only form of authentication is access to the home network, if the adversary can get into the network they can perform these attacks.  For example, if the user has an open WiFi network, then anyone nearby can launch this attack - potentially peforming a sort of drive-by deanonymization.  Similarly, the Safeplug would be utterly ineffective at securing traffic from a public network such as a hotel or cafe because every logged in user on that network could change the settings.

@@

\subsection{Gaining Access through SSH}
\label{sec:SSH}
    Another command available to the RPC server is enabling SSH to the device.  SSH instructions for Pogoplug's other device (called Pogoplug) are widely available online and an email in the Tor-talk mailing list confirms that the instructions are the same \cite{ceadmin}:
\begin{lstlisting}
curl --data ``'' http://<IP>/svc/xspctrl/enableSSHD
ssh root@<IP-of-Safeplug>
password: ceadmin
\end{lstlisting}

@@

One type of client that deserves special attention is a non-Android mobile phone user.  Although the Tor Project publishes an Android app called Orbot on the Android Market, which is supported for Android versions 2.3 and later, there are no official Tor apps for iPhones or other non-Android devices~\cite{orbot,amorbot}.  Safeplug provides proxy functionality and instructions for Safari on the iPhone and Chrome on Android.  However, while this does supposedly give the option for more mobile users to make use of Tor, proxy configuation on mobile devices comes with significant usability issues.  For example, the proxying would only work while the user is on that wifi network that the Safeplug routes through.  If any data is sent over the cellular network or another wifi network, then the security of Tor is lost.  Additionally, the user may have to disable the proxy whenever they move to a different network, and remember to re-enable it when they want to use Tor.  This is certainly not transparent usability.  Users who are truly concerned about anonymity online should eschew the Safeplug and purchase a device that supports the Tor Browser Bundle or other Tor Project software.
